Choosing Color Palettes for Statistical Graphics

### 2006-05-29 trunk/vcd/paper/Color/draft.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@541 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=.8\textwidth}
\begin{figure}[p]
\begin{center}
<<votes, fig=TRUE, height=9, width=11>>=
votes <- votes[c(1, 3, 4, 5, 9, 11, 13, 14, 15, 16, 2, 6, 7, 8, 10, 12),]
votes <- votes[,c("CDU/CSU", "FDP", "SPD", "Gruene", "Linke")]
votes <- as.table(as.matrix(votes))
names(dimnames(votes)) <- c("", "")

mosaic(votes, labeling_args = list(rot_labels = c(0, 90, 0, 0), pos_labels = "center",
  just_labels = c("center", "center", "center", "right")),
  gp = gpar(fill = hcl(c(240, 60, 0, 120, 300), 60, 75)),
  spacing = spacing_highlighting, labeling = labeling_left,
  margins = unit(c(2.5, 1, 1, 12), "lines"), keep = FALSE)
@
\caption{\label{fig:votes} Votes in the German election 2005}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=.8\textwidth}
\begin{figure}[p]
\begin{center}
<<votes, fig=TRUE, height=9, width=11>>=
Votes <- as.table(as.matrix(votes[c(1, 3, 4, 5, 9, 11, 13, 14, 15, 16, 2, 6, 7, 8, 10, 12),c("CDU/CSU", "FDP", "SPD", "Gruene", "Linke")]))
names(dimnames(Votes)) <- c("", "")

mosaic(Votes, labeling_args = list(rot_labels = c(0, 90, 0, 0), pos_labels = "center",
  just_labels = c("center", "center", "center", "right")),
  gp = gpar(fill = hcl(c(240, 60, 0, 120, 300), 60, 75)),
  spacing = spacing_highlighting, labeling = labeling_left,
  margins = unit(c(2.5, 1, 1, 12), "lines"), keep = FALSE)
@
\caption{\label{fig:votes} Votes in the German election 2005}
\end{center}
\end{figure}
